Timeliness of security updates for Android

### 2014-10-28 securityupdates.tex
Tighten up discussion of iOS security

The security protections used in iOS such as only allowing signed code to run, jails and reviewing of apps has resulted in a lower level of malware affecting iOS~\cite{TODO} but can still be bypassed~\cite{Wang2013a}. \todo{look at iOS protections again and tighten this up}

>>>>

The security protections used in iOS such, app review, code signing, Data Execution Prevention (DEP) and Address Space Layout Randomisation (ASLR) and mandatory access controls has resulted in a lower level of malware affecting iOS~\cite{Felt2011} but can still be bypassed~\cite{Wang2013a}.
